---
title: "Basic Examples"
output: html_document
---

```{r}
library(ideogRam)
library(GenomicRanges)
```

## Human

A human genome is depicted below. The grey and black bands in each chromosome represent heterochromatin. The pink region is the area around the centromere, and the blue represents variable regions. 

```{r}
ideogRam(organism = "human", chrHeight = 500)
```

## Mouse

```{r}
ideogRam(
    organism = "mouse",
    orientation = "horizontal",
    showBandLabels = TRUE,
    chrHeight = 300
)
```

## Annotations, basic

The location of BRCA1 is depicted here in red.

```{r}
brca1 <- GRanges('17', IRanges(43044294, 43125482), name = "BRCA1")
# This seems a bug, as it shows chromosomes 1, 7 and 17.
ideogRam(organism = "human") %>%
    set_option(chromosomes = '17', chrHeight = 600, orientation = "horizontal") %>%
    set_option(showAnnotTooltip = TRUE) %>%
    add_track(brca1)
```

## Annotations, overlaid

Large-scale structural variations (SVs) can be depicted using colored overlays, as seen below.

```{r}
ten_virtual_cnvs <- ideogRam:::sample_10_virtual_cnvs()
ten_virtual_cnvs
ideogRam(organism = "human") %>%
    set_option(chrHeight = 300, chrMargin = 2, annotationsLayout = "overlay",
               orientation = "horizontal") %>%
    add_track(ten_virtual_cnvs)
```

## Annotations, tracks


## Layout, small


```{r}
ideogRam(organism = "human", orientation = "vertical", rows = 2) %>%
    set_option(resolution = 550, chrHeight = 150, rotatable = FALSE)
```

## Brush

```{r}
ideogRam(
    organism = "human",
    chromosome = "1",
    resolution = 550,
    chrHeight = 600,
    orientation = "horizontal",
    brush = TRUE  ## In the new version, we need to give a string
)
```

## Ploidy, basic

```{r}
ideogRam(
    organism = "human",
    sex = "female",
    chrHeight = 300,
    chrWidth = 8,
    ploidy = 2
)
```



## Selected genes

Some random selected genes from EnsDb

```{r}
library(EnsDb.Hsapiens.v75)
set.seed(1)
genes <- genes(EnsDb.Hsapiens.v75)
genes <- genes[start(genes) < 40000000]
genes <- genes[sample(seq(length(genes)), 100)]

p <- ideogRam(organism = "human") %>%
    set_option(orientation = "vertical", chrHeight = 300) %>%
    add_track(genes)
p
```
